Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (uniform distribution)

### 2023-03-05 Manual.Rmd
updated manual with adding link for article_plots

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_PR_TV_Uni_mMSE.pdf** and **SMSE_MI_PR_TV_Uni_mVc.pdf**.

>>>>

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **Article_Plots/SMSE_MI_PR_TV_Uni_mMSE.pdf** and **Article_Plots/SMSE_MI_PR_TV_Uni_mVc.pdf**.
